---
title: "Question 3"
output: html_document
---

```{r}
library(tidyverse)
```

It is an chance for you to practice your skills on regular expressions.


(a) Consider the `phones.txt` files, extract all the telephone/fax numbers and format them as `(xxx)-xxx-xxxx`. (Hint: there should be 24 of them.)

```{r}
txt <- read_file("phones.txt")
```


(b) Write a regular expression `regex` that will match valid urls (the urls in `strings` are valid and none of the `strings2` are valid urls). Your regex should be as general as possible, do not hard code the domain names.

```{r}
strings <- c(
    "http://www.foufos.gr",
    "https://www.foufos.gr",
    "http://foufos.gr",
    "http://www.foufos.gr/kino",
    "http://werer.gr",
    "www.foufos.gr",
    "www.mp3.com",
    "www.t.co",
    "http://t.co",
    "http://www.t.co",
    "https://www.t.co",
    "www.aa.com",
    "http://aa.com",
    "http://www.aa.com",
    "https://www.aa.com",
    "https://www.aa.com"
)
strings2 <- c(
    "www.foufos",
    "www.foufos-.gr",
    "www.-foufos.gr",
    "foufos.gr",
    "http://www.foufos",
    "http://foufos",
    "www.mp3#.com"
)
```

```{r}
regex <- ""
all(str_detect(strings, regex))
all(str_detect(strings2, regex, negate = TRUE))
```

